Twists of supersymmetric gauge theories

### 2019-09-10 paper.tex
Actions of Lie algebras on field theories

Throughout the paper we will mostly work with a $\ZZ\times\ZZ/2$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.

@@

We call $\cE$ the {\em space of BV fields}.  
The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted bracket, in the following way.
In Section 3 of \cite{CosRenorm}, it is shown that to every {\em local} functional $f \in \cO(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$. 
Note that if $f$ is degree $n$, then $X_f$ is of degree $n+1$ due to the degree of $\omega$.

\begin{definition}
The {\bf BV antibracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
\[
\{-,-\} : \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE)
\]
defined by sending a pair $(f,g)$ to the local functional $X_f (g)$.
\chris{Also cite \cite{WittenAntibracket}.}
\end{definition}

This pairing is graded symmetric and satisfies the graded Jacobi identity.
Note that since local functionals do not form an algebra, it is not a (shifted) Poisson bracket.

@@

\chris{The idea, and a description of the kind of infinitesimal symmetries we're talking about (maybe just by a super Lie algebra in this paper, although we allow $L_\infty$ actions).  More generally we might consider the action of general local $L_\infty$ algebras.}

\begin{definition} \label{infinitesimal_action_def}
Let $(E, Q,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras (in differentiable pro-cochain complexes)
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\end{definition}

We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes (see Appendix \ref{appx:infinity}).
\brian{Is there a reason $\rho_2$ is the linear map. I'd thought $\rho_1$...}

Concretely, an action $\rho$ of a super dg Lie algebra $\fg$ on a classical field theory is given by an element
\[I_{\rho} = \sum_{k\geq 1} I_{\rho}^{(k)}\in \oloc(E)\otimes \widehat{\sym}^{\geq 1}(\fg^*[-1])\]
which satisfies the Maurer--Cartan equation
\[\{S_{\mr{BV}}, I_\rho^{(k+1)}\} + \d_{CE} I_{\rho}^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I_{\rho}^{(a)}, I_{\rho}^{(b)}\} = 0\]
for every $k\geq 0$.

\begin{definition}
\chris{The definition of the Chevalley-Eilenberg complex with coefficients, in particular the cup product / bracket, with its correct sign.  Pavel suggested saying that $C^\bullet(\gg; V) = \hom(\sym^\bullet(\gg[1]), V)$, and following the sign rule he used in \cite[Section 2.1]{SafronovCoisoInt}.}
\end{definition}

\begin{definition}
\chris{The definition of the equivariant observables in a classical BV theory with a symmetry as the relative Chevalley Eilenberg complex with coefficients in local functionals, with its anti-bracket.}
\end{definition}

\begin{remark}
\chris{Remark on the d\'ecalage isomorphism with a reference, then give an interpretation of the relative Chevalley-Eilenberg complex after applying this isomorphism as the inclusion of background fields valued in the constant sheaf with value $\gg$.}
\end{remark}

\chris{mention smooth group actions, with a reference.}

@@

@@

\begin{comment}
\brian{should we make these definitions, recollections, or just conventions?}

If $M$ is a smooth manifold, its {\em de Rham stack}, as a dg ringed space, is 
\[
M_{\rm dR} = \left(M , (\Omega^\bu_M, \d_{\rm dR})\right) .
\]

If $X$ is a complex manifold, there are two naturally associated dg ringed spaces that will be important for us. 
The first is the $\dbar$-{\em stack}, defined by
\[
X_{\dbar} = \left(M , (\Omega^{0,\bu}_X, \dbar) \right) .
\]
The next is the {\em Dolbeault stack}, defined by
\[
X_{\rm Dol} = \left(M, (\Omega^{\bu,\bu}_X, \dbar)\right) .
\] 
Note that as sheaves of dg modules, there is a quasi-isomorphism $(\Omega^{p,*}_M, \dbar) = \Omega^{p, hol}_M$.
Thus, one can think of the underlying ring of the Dolbeault stack as functions on the shifted holomorphic tangent bundle $T^{1,0} [1] M$ of $M$.
\end{comment}

@@

\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$, where every field is considered even with respect to the $\ZZ/2$-grading. $F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.

@@

Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$-system.

@@

\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$, where every field is considered even with respect to the $\ZZ/2$-grading. $F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.

@@

\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$, where every field is considered even with respect to the $\ZZ/2$-grading.

@@

Let us now give an example of a theory which is not partially holomorphic. We will give a general description of the Yang--Mills theory on $M=\RR^n$ with adjoint spinorial matter. Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(n; \CC)$ with an $\so(n)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to \CC^n$ (see Section \ref{sec: susy} for more details on supersymmetry). The fields of super Yang--Mills theory are the following:
\begin{itemize}
\item A connection $A \in \Omega^1(\RR^n; \fg)$ on the trivial bundle.

\item A section $\lambda \in \Omega^0(\RR^n; \Pi \Sigma \otimes \fg)$.

\item The ghost field $c\in\Omega^0(\RR^n; \fg)[1]$.
\end{itemize}

Thus, the bundle of BRST fields is
\[F = (\Omega^1(M)\oplus \Omega^0(M; \Pi\Sigma)\oplus \Omega^0(M)[1])\otimes \fg.\]
The corresponding local super dg Lie algebra $L=F[-1]$ is
\[
L \;\;\; = \begin{array}{ccccc}
& \ul{0} & & \ul{1} & \\ 
& & & & \\
& \Omega^0(M; \gg) & \to & \Omega^1(M; \gg) \oplus \Omega^0(M; \Pi \Sigma \otimes \gg) & 
\end{array}
\]
whose differential is the de Rham differential $\Omega^0(M; \gg)\rightarrow \Omega^1(M; \gg)$ and the bracket is induced from the Lie bracket on $\gg$.

@@

The BRST action is given by
\[S(A, \lambda) = \int_M \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle.\]

The associated BV theory $(E, Q, \omega, I)$ is given as follows (see also \cite[Section 3.1]{ElliottYoo1}). Let $A^*, \lambda^*, c^*$ be the antifields corresponding to $A, \lambda, c$ respectively. The bundle of BV fields is
\[E = \Omega^1(M; \fg)\oplus \Omega^0(M; \Pi\Sigma\otimes \fg)\oplus \Omega^0(M; \fg)[1] \oplus \Omega^{n-1}(M; \fg^*)[-1]\oplus \Omega^n(M; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(M; \fg^*)[-2].\]
The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
\[S_{BV} = \int_M \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle + (A^*, \d_A c) + (\lambda^*, [\lambda, c]).\]

We'll conclude this section with a discussion of the Poincar\'e invariance of classical Yang-Mills theory.

\begin{definition}
The $n$-dimensional {\bf Poincar\'e group} is the group $\mr{ISO}(n) = \SO(n) \ltimes \RR^n$ of isometries of $\RR^n$ with its flat Riemannian metric.  The $n$-dimensional {\bf Poincar\'e algebra} $\mf{iso}(n)$ is the Lie algebra of the Poincar\'e group.
\end{definition}

The $n$-dimensional Poincar\'e algebra acts, in the sense of Definition \ref{infinitesimal_action_def}, on Yang--Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation.
\chris{define the interaction functional $I_\mr{Poin}$ associated to the Poincar\'e action on Yang-Mills theory.}

\begin{prop} \label{YM_Poincare_invariant_prop}
Yang--Mills theory is \emph{Poincar\'e invariant}.  That is, the classical BV action functional satisfies the Maurer-Cartan equation
\[\{S_{BV}, I_{\mr{Poin}}\} + \d_{CE} I_{\mr{Poin}} + \frac 12 \{I_{\mr{Poin}}, I_{\mr{Poin}}\} = 0.\]
\end{prop}
\begin{proof}
\chris{...}
\end{proof}

@@

>>>>

Throughout the paper we will mostly work with a $\ZZ\times\ZZ/2$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading. For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.

@@

We call $\cE$ the {\em space of BV fields}.  
The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted bracket, in the following way.
In \cite[Chapter 5, Section 3]{CostelloBook}, it is shown that to every {\em local} functional $f \in \cO(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$. 
Note that if $f$ is degree $n$, then $X_f$ is of degree $n+1$ due to the degree of $\omega$.

\begin{definition}
The {\bf BV bracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
\[
\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE)
\]
defined by sending a pair $(f,g)$ to the local functional $X_f (g)$.
\end{definition}

The BV bracket satisfies the symmetry property
\[\{f, g\} = (-1)^{|f| |g|} \{g, f\}\]
and the graded Jacobi identity. Note that since local functionals do not form an algebra, it is not a (shifted) Poisson bracket.

@@

In this section we define what it means for a Lie algebra to act on a classical field theory. Let $(E, Q,\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra. Consider the graded vector space
\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n).\]
We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
and the BV bracket by the formula
\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]

\begin{definition}
\label{infinitesimal_action_def}
Let $(E, Q,\omega, I)$ be a classical field theory. An {\bf action} of a super Lie algebra $\fg$ on $(E, Q, \omega, I)$ is an element
\[I_{\rho} = \sum_{k\geq 0} I^{(k)}\in C^\bullet(\fg, \oloc(\cE)),\]
where $I^{(0)} = I$ and $I^{(k)}\colon \fg^{\otimes k}\rightarrow \oloc(\cE)$, which satisfies the Maurer--Cartan equation
\[(Q + \d_{CE}) I_\rho + \frac{1}{2} \{I_\rho, I_\rho\} = 0.\]
\end{definition}

We may also define actions of supergroups on classical field theories.

\begin{definition}
\label{group_action_def}
Let $(E, Q, \omega, I)$ be a classical field theory. An {\bf action} of a supergroup $G$ on $(E, Q, \omega, I)$ is an action of $G$ on $\cE$ preserving the symplectic pairing $\omega$, differential $Q$ and $I$ together with an action $I_\rho$ of its super Lie algebra $\fg$ with $I^{(k)} = 0$ for $k\geq 2$ such that for every $x\in\fg$ the vector field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
\end{definition}

\begin{remark}
While we allow for $L_\infty$ actions of Lie algebras, we only consider strict actions of Lie groups.
\end{remark}

@@

If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
\[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]

@@

In this section we give some examples of classical field theories we will use. All theories we consider in this section except for the Yang--Mills theory are $\ZZ$-graded, i.e. all fields are considered even with respect to the $\ZZ/2$-grading.

@@

\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$. $F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.

@@

Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$ system.

@@

\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$. $F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.

@@

\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.

@@

Let us now give an example of a theory which is not partially holomorphic. We will give a general description of the Yang--Mills theory on a vector space $V_\RR = \RR^n$ with adjoint spinorial matter. Denote by $V=V_\RR\otimes_\RR \CC$ its complexification.

Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$ (see Section \ref{sec: susy} for more details on supersymmetry). The fields of super Yang--Mills theory are the following:
\begin{itemize}
\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.

\item A section $\lambda \in \Omega^0(V_\RR; \Pi \Sigma \otimes \fg)$.

\item The ghost field $c\in\Omega^0(V_\RR; \fg)[1]$.
\end{itemize}

Thus, the bundle of BRST fields is
\[F = (\Omega^1(V_\RR)\oplus \Omega^0(V_\RR; \Pi\Sigma)\oplus \Omega^0(V_\RR)[1])\otimes \fg.\]
The corresponding local super dg Lie algebra $L=F[-1]$ is
\[
L \;\;\; = \begin{array}{ccccc}
& \ul{0} & & \ul{1} & \\ 
& & & & \\
& \Omega^0(V_\RR; \gg) & \to & \Omega^1(V_\RR; \gg) \oplus \Omega^0(V_\RR; \Pi \Sigma \otimes \gg) & 
\end{array}
\]
whose differential is the de Rham differential $\Omega^0(V_\RR; \gg)\rightarrow \Omega^1(V_\RR; \gg)$ and the bracket is induced from the Lie bracket on $\gg$.

@@

The BRST action is given by
\[S(A, \lambda) = \int_{V_\RR} \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle.\]

The associated BV theory $(E, Q, \omega, I)$ is given as follows (see also \cite[Section 3.1]{ElliottYoo1}). Let $A^*, \lambda^*, c^*$ be the antifields corresponding to $A, \lambda, c$ respectively. The bundle of BV fields is
\[E = \Omega^1(V_\RR; \fg)\oplus \Omega^0(V_\RR; \Pi\Sigma\otimes \fg)\oplus \Omega^0(V_\RR; \fg)[1] \oplus \Omega^{n-1}(V_\RR; \fg^*)[-1]\oplus \Omega^n(V_\RR; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(V_\RR; \fg^*)[-2].\]
The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
\[S_{BV} = \int_{V_\RR} \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle + (A^*, \d_A c) + (\lambda^*, [\lambda, c]).\]

We conclude this section with a discussion of the Poincar\'e invariance of classical Yang--Mills theory.

\begin{definition}
The {\bf Poincar\'e group} is $\mr{ISO}(V_\RR) = \Spin(V_\RR) \ltimes \RR^n$. The {\bf Poincar\'e algebra} is its complexified Lie algebra $\mf{iso}(V)$.
\end{definition}

The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation. Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$. The corresponding Hamiltonian is given by
\[
I_{\mr{Poin}}(v) = \int_{V_\RR} (v.A) \wedge A^* + (v.\lambda) \lambda^* + (v.c)c^*,
\]
where $v\in\mf{iso}(V)$.

@@

\subsection{Supersymmetry algebras}
